Supporting Information: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-20 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
coments on supporting information.

  % mimic this
  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function. \\\hline
  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
  \texttt{/analysis/ markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline

  \end{tabular}

@@

  % /supporting_figures/hurst_autocorrelation.py
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hurst_autocorrelation.pdf}
  \caption{}\label{fig:hurst_autocorrelation}
  \end{subfigure}
  % supporting_figures/flm_autocov.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flm_autocovariance.pdf}
  \caption{}\label{fig:flm_autocorrelation}
  \end{subfigure}
  \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
  when H $<$ 0.5 compared to when H $>$ 0.5. (b) The autocorrelation function of an 
  FLM process does not change with increasing sequence length (N). It shares the same
  autocorrelation function as fractional Brownian motion (FBM). All sequenced used to
  make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
  \end{figure}

@@

  \textit{Determining where to truncate the hop distribution:} A pure
  L\'evy stable distribution has heavy tails which can lead to arbitrarily
  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
  distribution near the mean, but under samples the tails. In 
  Figure~\ref{fig:truncation_correction} we compare the empirically 
  measured transition emission distribution of the MSDDM for urea to its maximum likelihood fit to
  a L\'evy stable distribution. The ratio between the two distributions 
  at each bin is nearly 1 close to the center, indicating a near-perfect
  fit, larger than 1 slightly further from the center, suggesting that 
  we slightly over sample intermediate hop lengths, and below 1 far from 
  the center, indicating under sampling of extremely long hop lengths.
  Based on the plot, we chose a cut-off of 1 nm in order to compensate for
  over sampled intermediate hop lengths. We chose the same cut-off for all
  solutes.

  \begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{truncation_cutoff.pdf}
  \caption{The ratio between the empirical and maximum likelihood theoretical
  distribution quantifies the quality of fit as function of hop length. The fit
  is near-perfect close to the mean. Intermediate hop lengths are over sampled, 
  and the tails are under sampled. We used this type of plot to determine the
  appropriate place to truncate the L\'evy stable distributions.}\label{fig:truncation_cutoff}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_counts.pdf}
  \caption{Urea}\label{fig:URE_counts}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_counts.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_counts}
  \end{subfigure}
  \caption{The number of transitions from state $i$ to $j$ and $j$ to $i$ are very close
  indicating that our process obeys detailed balance. Detailed balance is conserved for 
  different sized time steps.}\label{fig:counts}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_transitions.pdf}
  \caption{Urea}\label{fig:URE_transitions}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_transitions.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_transitions}
  \end{subfigure}
  \caption{As the timestep between observations increases, the probability
  transition matrix does not change signficantly.}\label{fig:transitions}
  \end{figure}

@@

  Analagous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
  same kind of anti-correlated hopping and trapping behavior.

@@

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calcluated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajctories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
  \end{subfigure} 
  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
  %BJC6: I think red and orange are directly on top of each other with same error bars
  \caption{In most cases, when using power laws with exponential cut-offs 
  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
  the first half of the equilibrated data lie within the 1$\sigma$ confidence
  intervals of the MD MSD curves generated from the second half of the equilibrated
  solute data. The models which use pure power laws systematically under-predict
  the MD MSD curves. Over and under-estimated curvature of the of urea and acetic acid's 
  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
  under-predicted at long timescales and those of acetic acid to be under-predicted
  at short timescales.}\label{fig:train_test}
  \end{figure}

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of Urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories. Considering the longest observed dwell time among all
  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
  %It is not clear whether this is a consistent feature of the AD model since we 
  %only used 2 solutes for this analysis.

@@

  From a qualitative perspective, the models only have moderate success at predicting
  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
  the error in the predicted MSD magnitudes. The curves predicted for Urea with both 1 
  and 2 modes appear to have too much curvature, which causes it to under-predict the 
  MSD at long timescales, while those of acetic acid lack curvature, leading the
  AD model to under-predict the MSD at short timescales.

  The under-estimate of Urea's MSD at long timescales is due to long timescale
  positional anti-correlation which may not be present in the molecularly 
  detailed simulations of the system. The 
  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
  %but perhaps I'm misunderstanding something here? 
  persistent curvature of the predicted MSD curves is a direct consequence of 
  the Hurst parameter. Without anti-correlation, the process would be 
  a pure CTRW for which one would expect the time averaged MSD curves to become 
  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
  positional correlation is lost which would manifest as a transition from a sub-linear
  to linear MSD curve. A solution for more accurately modeling this behavior in  
  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}

@@

  \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}

  The tables in the section are tabular representations of the parameters depicted
  in Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the 
  main text.

  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

@@

  \section{Tabular MSDDM parameters}\label{section:msddm_params}

@@

  In Figures~\ref{fig:ad_fpt_fits} and~\ref{fig:msddm_fpt_fits}, we demonstrate
  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
  the distribution of solute first passage times derived from both the AD
  and MSDDM models. The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
  relatively noisy because we only generated 1000 realizations of the MSDDM 
  versus 10000 of the AD model. In Figure~\ref{fig:flux_curve_sensitivity}, we
  justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
  model realizations to show that one needs as few as 100 independent trajectory
  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
  to the passage time distributions.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
  \caption{100 Independent Trajectories}\label{fig:N100}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
  \caption{1000 Independent Trajectories}\label{fig:N1000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
  \caption{5000 Independent Trajectories}\label{fig:N5000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
  \caption{10000 Independent Trajectories}\label{fig:N10000}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably calculate flux as a function of pore length. The uncertainty in
  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
  \end{figure}

  % equations here 
  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf

@@

%  Suprisingly, $\beta$ is still close to the Brownian value. Further experimentation 

@@

%  %MRS6: should try to lead with what the overall results/conclusions are.  What does it mean that parameters are larger or smaller?  What should the reader take from the discussion?  Should it be in supportinig?

@@

>>>>

  % mimic this
  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function. \\\hline
  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
  \texttt{/analysis/ Markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline
%MRS8: see main text discussion about ``the XXXX model''  
  \end{tabular}

@@

  % /supporting_figures/hurst_autocorrelation.py
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hurst_autocorrelation.pdf}
  \caption{}\label{fig:hurst_autocorrelation}
  \end{subfigure}
  % supporting_figures/flm_autocov.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flm_autocovariance.pdf}
  \caption{}\label{fig:flm_autocorrelation}
  \end{subfigure}
  %MRS8: make clear in (b) the lines all lay on top so people don't miss it.  
  \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
  when H $<$ 0.5 compared to when H $>$ 0.5. (b) The autocorrelation function of an 
  FLM process does not change with increasing sequence length (N). It shares the same
  autocorrelation function as fractional Brownian motion (FBM). All 
  %sequenced
  sequences 
  used to
  make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
  \end{figure}

@@

  \textit{Determining where to truncate the hop distribution:} A pure
  L\'evy stable distribution has heavy tails which can lead to arbitrarily
  long hop lengths. Our distribution of hop lengths fits well to a L\'evy
  distribution near the mean, but under-samples the tails. In 
  Figure~\ref{fig:truncation_correction} we compare the empirically 
  measured transition emission distribution of the MSDDM for urea to its maximum likelihood fit to
  a L\'evy stable distribution. The ratio between the two distributions 
  at each bin is nearly 1 close to the center, indicating a near-perfect
  fit, larger than 1 slightly further from the center, suggesting that 
  we slightly over sample intermediate hop lengths, and below 1 far from 
  the center, indicating undersampling of extremely long hop lengths.
  Based on the plot, we chose a cut-off of 1 nm in order to compensate for
  over sampled intermediate hop lengths. We chose the same cut-off for all
  solutes.

  \begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{truncation_cutoff.pdf}
  \caption{The ratio between the empirical and maximum likelihood theoretical
  distribution quantifies the quality of fit as function of hop length. The fit
  is near-perfect close to the mean. Intermediate hop lengths are over sampled, 
  and the tails are undersampled. We used this type of plot to determine the
  appropriate place to truncate the L\'evy stable distributions.}\label{fig:truncation_cutoff}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_counts.pdf}
  \caption{Urea}\label{fig:URE_counts}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_counts.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_counts}
  \end{subfigure}
  \caption{The number of transitions from state $i$ to $j$ and $j$ to $i$ are very close
  indicating that our process obeys detailed balance. Detailed balance is conserved for 
  different sized time steps.}\label{fig:counts}
  %MRS: would this be clearer to see if you plotted i-j/i+j for a relative error to see how different it is from symmetric jumps? 
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_transitions.pdf}
  \caption{Urea}\label{fig:URE_transitions}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_transitions.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_transitions}
  \end{subfigure}
  \caption{As the timestep between observations increases, the probability
  transition matrix does not change significantly.}\label{fig:transitions}
  \end{figure}

@@

  Analogous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
  same kind of anti-correlated hopping and trapping behavior.

@@

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calculated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajectories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
  \end{subfigure} 
  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
  %BJC6: I think red and orange are directly on top of each other with same error bars
  %MRS8: point out that the _cut data is the same as the data in the main tex. 
  \caption{In most cases, when using power laws with exponential cut-offs 
  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
  the first half of the equilibrated data lie within the 1$\sigma$ confidence
  intervals of the MD MSD curves generated from the second half of the equilibrated
  solute data. The models which use pure power laws systematically under-predict
  the MD MSD curves. Over- and under-estimated curvature of the of urea and acetic acid's 
  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
  under-predicted at long timescales and those of acetic acid to be under-predicted
  at short timescales.}\label{fig:train_test}
  \end{figure}

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories. Considering the longest observed dwell time among all
  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
  %It is not clear whether this is a consistent feature of the AD model since we 
  %only used 2 solutes for this analysis.

@@

  From a qualitative perspective, the models only have moderate success at predicting
  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
  the error in the predicted MSD magnitudes. The curves predicted for urea with both 1 
  and 2 modes appear to have too much curvature, which causes it to under-predict the 
  MSD at long timescales, while those of acetic acid lack curvature, leading the
  AD model to under-predict the MSD at short timescales.

  %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
  The under-estimate of urea's MSD at long timescales is due to long timescale
  positional anti-correlation which may not be present in the molecularly 
  detailed simulations of the system. The 
  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
  %but perhaps I'm misunderstanding something here? 
  persistent curvature of the predicted MSD curves is a direct consequence of 
  the Hurst parameter. Without anti-correlation, the process would be 
  a pure CTRW for which one would expect the time averaged MSD curves to become 
  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
  positional correlation is lost which would manifest as a transition from a sub-linear
  to linear MSD curve. A solution for more accurately modeling this behavior in  
  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}

@@

  %MRS8: I think just ``Tables of Anomalous''.  Tabular sounds like it's a kind of anomalous diffusion.
  \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}

  %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
  The tables in the section are tabular representations of the parameters depicted
  in Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the 
  main text.

  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  %MRS: to what extent are these captions the same as the captions to equivalent graphs main text?  If it's the same, you probably should say so; if different, there should be some justification for the differences, and should be mentioned in the main text that more information is here. 
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

@@

  \newpage
  %MRS8: ``Table of''. Same comments about captions being the same or different, since the data should be the same.
  \section{Tabular MSDDM parameters}\label{section:msddm_params}

@@

  %MRS8: See discussion in main text on ``the AD model''
  %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
  In Figures~\ref{fig:ad_fpt_fits} and~\ref{fig:msddm_fpt_fits}, we demonstrate
  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
  the distribution of solute first passage times derived from both the AD
  and MSDDM models. The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
  relatively noisy because we only generated 1000 realizations of the MSDDM 
  versus 10000 of the AD model. In Figure~\ref{fig:flux_curve_sensitivity}, we
  justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
  model realizations to show that one needs as few as 100 independent trajectory
  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
  to the passage time distributions.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
  \caption{100 Independent Trajectories}\label{fig:N100}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
  \caption{1000 Independent Trajectories}\label{fig:N1000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
  \caption{5000 Independent Trajectories}\label{fig:N5000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
  \caption{10000 Independent Trajectories}\label{fig:N10000}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably calculate flux as a function of pore length. The uncertainty in
  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
  \end{figure}
  %MRS8: is there a way to make it easier to see the fact that the data is relatively independent of length?
  %MRS8: Right now, you essentially have to scan between the 4 charts to see the numbers are about right. Maybe
  %MRS8: organize it so that the 4 charts are for 4 molecules, and each chart shows plot of 
  %MRS8: trajectory number vs pore length, so one can see that the value stays about the same except for uncertainty as 
  %MRS8: number of trajectories changes
  % equations here 
  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf

@@

%  Surprisingly, $\beta$ is still close to the Brownian value. Further experimentation 

@@

%  %MRS6: should try to lead with what the overall results/conclusions are.  What does it mean that parameters are larger or smaller?  What should the reader take from the discussion?  Should it be in supporting?

@@

% LocalWords:  LLC solutes py equispaced solute's ctrw sfbm ctrwsim MSD solute
% LocalWords:  MSDDM XXXX GitHub plateaued Meroz Sokolov superdiffusion MSDs wt
% LocalWords:  subdiffusion msd PR nojump xtc gro ETH nboot pdf subdiffusive xr
% LocalWords:  RWF brownian FBM CTRWs traj npt fracshow Taqqu recentering MFPT
% LocalWords:  Markovianity timestep GCL acf ACH bothmode params BJC tex acid's
% LocalWords:  sFBMcut sFLMcut urea's timescale msddm fpt CDF mfpt cdf hurst
% LocalWords:  decorrelate
